### 2022-04-01 GB_Simulation_3Species.Rmd
Updates

@@

@@

STILL NEED: START CELL, REC PARAMS, K GROWTH PARAMS

#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = c(42,155),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), #CORRECT FOR YTF
                     M = c("spp1" = 0.25+0, "spp2" = 0.35+0, "spp3" = 0.2+.05), #CHANGE
                     K = c("spp1" = 0.3, "spp2" = 0.3, "spp3" = 0.3), #CHANGE
                     nz = nonzero_idx)

@@

#set lambda at 0 first, change after initial population set
Pop$dem_params$spp1$lambda <- .1

@@

fields::image.plot(Pop$Start_pop[[1]], main = "spp1 starting biomass")

@@

#no fishing
fleets <- init_fleet(sim_init = sim, VPT = list("spp1" = 0, "spp2" = 0), #VPT = value per ton
                     Qs = list("fleet 1" = c("spp1" = 0, "spp2" = 0)   #Q = catchability
                     ),
                     fuelC = list("fleet1" = 3),
                     step_params = list("fleet 1" = c("rate" = 3, "B1" = 1, "B2" = 2, "B3" = 3)
                     ),				
                     past_knowledge = FALSE,  #dont use past knowledge
                     past_year_month = TRUE,
                     past_trip = TRUE,
                     threshold = 0.7
)

@@

>>>>

hab <- readRDS("hab_GB_3species.RDS")

@@

##where should starting point be? check highest values locations
# which(hab[["hab"]][["spp1"]]==max(hab[["hab"]][["spp1"]],na.rm=T),arr.ind=T)
# which(hab[["hab"]][["spp2"]]==max(hab[["hab"]][["spp2"]],na.rm=T),arr.ind=T)
# which(hab[["hab"]][["spp3"]]==max(hab[["hab"]][["spp3"]],na.rm=T),arr.ind=T)
# 
# #make sure each have nonzero value on start cell
# hab[["hab"]][["spp1"]][46,112]
# hab[["hab"]][["spp2"]][30,134]
# hab[["hab"]][["spp3"]][24,91]

@@

STILL NEED: REC PARAMS, K GROWTH PARAMS

Recr(model = "BH", params = list("a" = 1000, "b" = 450),
   B = max(Pop[["Start_pop"]][["spp1"]],na.rm=T), cv = 0)

#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), #CORRECT FOR YTF
                     M = c("spp1" = 0.25+0, "spp2" = 0.35+0, "spp3" = 0.2+.05), #CHANGE
                     K = c("spp1" = 0.3, "spp2" = 0.3, "spp3" = 0.3), #CHANGE
                     nz = nonzero_idx)

@@

#set lambda at 0 first, change after initial population set
Pop$dem_params$spp1$lambda <- .1
Pop$dem_params$spp2$lambda <- .1
Pop$dem_params$spp3$lambda <- .1

@@

fields::image.plot(Pop$Start_pop[[1]], main = "spp1 starting biomass")
fields::image.plot(Pop$Start_pop[[2]], main = "spp1 starting biomass")
fields::image.plot(Pop$Start_pop[[3]], main = "spp1 starting biomass")

@@

#no fishing
fleets <- init_fleet(sim_init = sim, VPT = list("spp1" = 0, "spp2" = 0, "spp3" = 0), #VPT = value per ton
                     Qs = list("fleet 1" = c("spp1" = 0, "spp2" = 0, "spp3" = 0)   #Q = catchability
                     ),
                     fuelC = list("fleet1" = 3),
                     step_params = list("fleet 1" = c("rate" = 3, "B1" = 1, "B2" = 2, "B3" = 3)
                     ),				
                     past_knowledge = FALSE,  #dont use past knowledge
                     past_year_month = TRUE,
                     past_trip = TRUE,
                     threshold = 0.7
)

@@

#   #rebuild package
devtools::build()
